---
title: "CHANGE TITLE AFTER ANALYSIS!"
author: "Landon Power"
date: last-modified
format: 
  html:
    editor: visual
    toc: true
    toc_float: true
    number-sections: true
    embed-resources: true
    date-format: iso
    theme: paper
---

# Setup and Data Ingest

## Setup

```{r, message = FALSE, warning = FALSE}
library(janitor)
library(knitr)
library(magrittr)
library(broom)
library(naniar)
library(patchwork)
library(modelsummary)
library(pwr)
library(haven) # Package to ingest SAS transport files for 2017-2020 Pre-pandemic NHANES data
library(tidyverse)

source("data/Love-boost.R")

theme_set(theme_light())  # or use theme_set(theme_bw())
knitr::opts_chunk$set(comment=NA)
```

## Data Ingest

I ingested the demographic raw data from the NHANES 2017-2020 Pre-Pandemic Demographic data.

```{r}
# Initially save the data from the NHANES Pre-pandemic 2017-2020 SAS transport
#demographic <- haven::read_xpt("data/P_DEMO.xpt")

#saveRDS(demographic, "data/P_DEMO.Rds")

# Simply read the tibble after data are saved
demographic <- readRDS("data/P_DEMO.Rds")
```

I ingested the standard biochemistry panel raw data from the NHANES 2017-2020 Pre-Pandemic Laboratory data.

```{r}
# Initially save the data from the NHANES Pre-pandemic 2017-2020 SAS transport
#biochem <- haven::read_xpt("data/P_BIOPRO.xpt")

#saveRDS(biochem, "data/P_BIOPRO.Rds")

# Simply read the tibble after data are saved
biochem <- readRDS("data/P_BIOPRO.Rds")
```

Finally, I ingested the Alcohol Use raw data from the NHANES 2017-2020 Pre-Pandemic Questionnaire data.

```{r}
# Initially save the data from the NHANES Pre-pandemic 2017-2020 SAS transport
#alcohol <- haven::read_xpt("data/P_ALQ.xpt")

#saveRDS(alcohol, "data/P_ALQ.Rds")

# Simply read the tibble after data are saved
alcohol <- readRDS("data/P_ALQ.Rds")
```

# Cleaning the Data

I then merged the NHANES files before cleaning and selecting my variables.

```{r}
full_uncleaned1 <- left_join(demographic, biochem, by = "SEQN")
```

```{r}
full_uncleaned2 <- left_join(full_uncleaned1, alcohol, by = "SEQN")
```

Then I cleaned the variables and selected only the variables I will use in analysis. I first cleaned the names of all the variables in the `full_uncleaned2` dataset.

```{r}
full <- full_uncleaned2 %>%
  clean_names() %>%
  mutate(across(where(is_character), as_factor))
```

I then selected the variables I will analyze and refined the observations to include only subjects who:

-   had a `ridstatr` value of 2, meaning they were both interviewed and examined (N = 14,300)

-   had a `ridageyr` between 21 and 79 years old (N = 7,853)

For my analysis, I then filtered to the proper variables I will analyze:

-   Analysis A: two quantitative variables

    -   alanine aminotransferase (ALT, in U/L)

    -   aspartate aminotransferase (AST, in U/L)

-   Analysis B: outcome (ALT) and binary categorical variable (gender)

-   Analysis C: outcome (ALT) and multi-categorical variable (Race/Hispanic origin)

-   Analysis E: J x K table of two categorical variables

    -   J (2-5 levels): Ever had 4/5 or more drinks every day? (2 levels, Yes/No)

    -   K (3-5 levels): Race/Hispanic origin (5 levels)

```{r}
liver_damage <- full %>%
  filter(ridstatr == "2") %>%
  filter(between(ridageyr, 21, 79)) %>%
  select(seqn, ridstatr, ridageyr, lbxsatsi, lbxsassi, 
         riagendr, ridreth1, alq151)

head(liver_damage)
```

# Codebook and Data Description

Continue here on 12/06/2024...
